Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
exp -> \exp in Eq 12

\gl{vincent, un petit mot pour motiver le fait que le scattering est un bon outil pour separer les evenements peuplant une scène sonore ?}.

@@

One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which performs some multivariate estimates over the whole dataset and not solely on each scene, and re-projects each scene in the resulting enhanced feature space.
Here, with the aim of balancing better the influence of salient events and texture-like sounds on the final decision, we consider several centroid-based similarity metrics between centroids:

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}
where $c_N$ is the $N^{\textrm{th}}$ nearest neighbor to the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

@@

%\ml{Grégoire : if the matrix is not psd, then this is NOT a kernel, reformulate}

>>>>

\gl{vincent, un petit mot pour motiver le fait que le scattering est un bon outil pour separer les evenements peuplant une scène sonore ?}. 
\vl{this section should be better segmented into subsections. The words centroid and cluster are defined after they are used. The order of paragraphs could be 1-4-3-2-5.}

@@

One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which performs some multivariate estimates over the whole dataset and not solely on each scene, and re-projects each scene in the resulting enhanced feature space.
Here, with the aim of balancing better the influence of salient events and texture-like sounds on the final decision, we consider several centroid-based similarity metrics:

@@

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = \exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation}
where $c_N$ is the $N^{\textrm{th}}$ nearest neighbor to the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

@@
